---
title: "assign4"
output: html_notebook
---
```{r}
library(lubridate)
library(stringr)
library(RVerbalExpressions)
library(dplyr)
```



For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
floor_date(today(), unit = "year") + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
# Enter input as year month day like --- 19980118
my_bd <- function(birthday) {
  as.numeric(as.duration(today() - ymd(birthday)), "years") %/% 1
}

my_bd(19980118)
```


Write a function that given your birthday, returns the day of the week you were born on. 
```{r}
# Enter input as year month day like --- 19980118
day_of_week <- function(birthday){
  wday(ymd(birthday),label=T)
}
day_of_week(19980118)

# Below is Python3 code ------
# def dayofweek(d, m, y):
#     t = [ 0, 3, 2, 5, 0, 3,
#           5, 1, 4, 6, 2, 4 ]
#     y -= m < 3
#     return (( y + int(y / 4) - int(y / 100)
#              + int(y / 400) + t[m - 1] + d) % 7)
# 
# day = dayofweek(18, 1, 1998)
# print(day)
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}
str_view(words, ".......", match = T)
str_subset(words, '.......')

```
```{r}
seven_and_more <- rx() %>% 
  rx_start_of_line() %>% 
  rx_alpha() %>% 
  rx_multiple(min = 7) 
  
str_subset(words,seven_and_more)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
str_subset(words,"^[^aeiou]+$")
```
```{r}
NotVowels <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but("aeiou") %>% 
  rx_multiple(min = 1) %>% 
  rx_end_of_line()

str_subset(words,NotVowels)
```


Empirically verify the rule “i before e except after c”.
```{r}
str_subset(words, "[^c]ie")
```
```{r}
ie_without_c <- rx() %>% 
  rx_avoid_prefix("c") %>% 
  rx_find("ie")

str_subset(words, ie_without_c)
```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
# format---- NXX-NXX-XXXX
# N=digits 2–9, X=digits 0–9
number <- "298-344-9437"
regex_1 <- "^[2-9]{3}-[2-9][0-9]{2}-[0-9]{4}$"
regex_2 <- "^[2-9]{3}.[2-9][0-9]{2}.[0-9]{4}$"
str_view(number,regex_1) 
```

```{r}
tel_verbal_expression <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() 

str_view(number,tel_verbal_expression)
```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

